Predictions for detecting BHNS and other double compact objects binaries with LISA

### 2021-03-24 paper/tex/paper.tex
add some supplementary figures
add NSNS trends and variation figures

\subsubsection{NSNS detection rate trends}\label{sec:NSNS_detection_trends}
\textbf{NSNS:} \todo{Why are B, C, D opposite?}. E is low because that's the main NSNS formation channel. CE follows nice trend (see Floor's about CE channels). Optimistic slightly up because duh. \todo{weirdly basically no change in rapid and max NS masses}. Lower kicks great as usual. No BH kicks no effect duh.

@@

Now talk about where they are on the sensitivity curve

@@

\section{Extra figures}

>>>>

\subsubsection{NSNS detection rate trends}\label{sec:NSNS_detection_trends}

\todo{understand the $\beta$ trends}. There is a drastic decrease in detections for model \modCaseBB{} by nearly two orders of magnitude. This is because the majority of NSNS binaries are formed through case BB mass transfer and setting this mass transfer to be always unstable results in many of these binaries to merge before they could become NSNSs. As a result the total number of detections decreases, however interestingly the remaining population represent more massive progenitors (that would not go through case BB mass transfer) and thus is skewed to higher masses and has a \textit{higher} detectable fraction (see Fig.~\ref{fig:detection_fractions}).

\todo{come back to CE ones once we understand the BHNS ones}. \todo{weirdly basically no change in rapid and max NS masses}. As we found in the BHNS trends, a lower value for the core-collapse supernova velocity dispersion increases the detection rate in models \modSigLow{} and \modSigLower{}, whilst changing the BH kick (model \modNoBH{}) of course has no effect on the NSNS population.

@@

\subsection{Distribution on the sensitivity curve}

@@

\section{Supplementary figures}

\subsection{Physics variation cumulative distributions}

\begin{figure*}[h]
    \centering
    \includegraphics[width=\textwidth]{variations_cdf_1_3.pdf}
    \caption{Cumulative distribution functions for the black hole mass, neutron star mass, eccentricity during the LISA mission and merger time for each DCO type and physics variation. In colour we show the fiducial populations compared to changing the mass transfer efficiency $\beta$. We additionally show the other physics variations in the background in light grey.}
    \label{fig:variations_cdf_1_3}
\end{figure*}

\begin{figure*}[h]
    \centering
    \includegraphics[width=\textwidth]{variations_cdf_4_6.pdf}
    \caption{As Fig.~\ref{fig:variations_cdf_1_3}, except comparing the fiducial population with models using different values for $\alpha_{\rm CE}$ and changing the stability of case BB mass transfer.}
    \label{fig:variations_cdf_4_6}
\end{figure*}

\begin{figure*}[h]
    \centering
    \includegraphics[width=\textwidth]{variations_cdf_7_10.pdf}
    \caption{As Fig.~\ref{fig:variations_cdf_1_3}, except comparing the fiducial population with models changing the maximum neutron star mass, remnant mass prescription and survivability of common envelope events initiated by Hertzsprung gap donors.}
    \label{fig:variations_cdf_7_10}
\end{figure*}

\begin{figure*}[h]
    \centering
    \includegraphics[width=\textwidth]{variations_cdf_11_14.pdf}
    \caption{As Fig.~\ref{fig:variations_cdf_1_3}, except comparing the fiducial population with models changing the core-collapse supernova kick distributions and the presence of BH kicks and PISNs.}
    \label{fig:variations_cdf_11_14}
\end{figure*}

\subsection{Detection rates}

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{dco_detections_fractions.pdf}
    \caption{As Figure~\ref{fig:detection_rates} except only showing the detectable \textit{fraction}.}
    \label{fig:detection_fractions}
\end{figure*}

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{dco_merging.pdf}
    \caption{The total number of merging DCOs in the Milky Way. When multiplied by Figure~\ref{fig:detection_fractions} this gives Figure~\ref{fig:detection_rates}.}
    \label{fig:total_merging_dcos}
\end{figure*}

\subsection{Miscellaneous}
